### 2024-11-12 Article/Background_sections/Limit.tex
introduction

    Since $((c_i')_{i \in \cat I}, C)$ is a limit by hypothesis, then must exists a unique arrow $c:C \to C'$ such that $c \circ c_i = \phi_i \circ c_i'$, having the thesis.
\end{proof}

@@

\begin{lemma}\label{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}
    Let $D, D': \cat{I \to C}$ be two diagrams, and let $((c_i)_{i \in \cat I}, C)$ and $((c_i')_{i\in \cat I}, C')$ be, respectively, the colimit of $D$ and $D'$. If $\cat C$ has all colimits, for diagrams of shape $\cat I$ and $phi: D \dot\to D'$ is a natural transformation in which all components are regular epimorphisms, then, the arrow induced by $\phi$ from $C$ to $C'$ (\Cref{prop:nat_tran_induces_unique_arrow_between_colimits}) is a regular epimorphism too.
\end{lemma}

>>>>

    Since $((c_i')_{i \in \cat I}, C)$ is a colimit by hypothesis, then must exists a unique arrow $c:C \to C'$ such that $c \circ c_i = \phi_i \circ c_i'$, having the thesis.
\end{proof}

@@

\begin{lemma}\label{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}
    Let $D, D': \cat{I \to C}$ be two diagrams, and let $((c_i)_{i \in \cat I}, C)$ and $((c_i')_{i\in \cat I}, C')$ be, respectively, the colimit of $D$ and $D'$. If $\cat C$ has all colimits, for diagrams of shape $\cat I$ and $\phi: D \dot\to D'$ is a natural transformation in which all components are regular epimorphisms, then, the arrow induced by $\phi$ from $C$ to $C'$ (\Cref{prop:nat_tran_induces_unique_arrow_between_colimits}) is a regular epimorphism too.
\end{lemma}

### 2024-11-12 Article/Graph_sections/Eq_Graphs_integration.tex
introduction

\begin{obs}\label{obs:eq_grph_morph_det_by_first_two_comp}
    Morphisms of graphs with equivalence are uniquely determined by the first two component. That is, if $h_1 = (h_E, h_V, \phi)$ and $h_2 = (h_E, h_V, \psi)$, then $\phi = \psi$.
\end{obs}

@@

	Therefore, the outer part of the rectangle below commutes, and by \Cref{prop:prop_epi_mono_Set} there exists a unique $\tau_C: G \to Q$
    \[
        \begin{tikzcd}
            F \arrow[r, "{\tau_V}"] \arrow[d, "c"swap] & B \arrow[r, "q"] & Q \arrow[d, "m"] \\
            G \arrow[urr, dashed, "{\tau_C}"] \arrow[rr, "{\tau}"swap] & & L
        \end{tikzcd}
    \]
     Faithfulness of $U$ guarantees that $(\tau_E, \tau_V, \tau_C)$ is the unique arrow such that $(\pi_E^i, \pi_V^i, \pi_C^i) \circ (\tau_E, \tau_V, \tau_C) = (\tau_E^i, \tau_V^i, \tau_C^i)$.
     \todo{Dimostrazione dello statement di sopra, e colimiti}

     For colimits, let $(A, B, s, t)$ be the colimit of $U \circ D$, together with morphisms $(\kappa_i)_{i \in \cat I} = (\kappa_E^i, \kappa_V^i)_{i \in \cat I}$, and suppose $((c_i)_{i \in \cat I}, C)$ be the colimit of $V \circ D$. Then, we have the following situation
     \[
	     \begin{tikzcd}[row sep = 25, column sep=25]
			& B & \\
			B_i \ar[rr, "{h_V}"] \ar[ur, "{\kappa_V^i}"] \ar[d, "{q_i}"swap] & & B_j \ar[ul, "{\kappa_V^j}"swap] \ar[d, "q_j"] \\
			C_i \ar[rr, "{h_C}" swap] \ar[dr, "{c_i}"swap] & & C_j \ar[dl, "{c_j}"] \\
			& C &
		\end{tikzcd}
     \]
     Then, $((c_i \circ q_i)_{i \in \cat I}, C)$ is a cocone for all $B_i$, and, since $((\kappa_i)_{i \in \cat I}, B)$ is the colimit of all $B_i$ (\Cref{lemma:limits_of_presheaves}), there exists a unique arrow $q: B \to C$ such that, for each $i$, $q \circ \kappa_V^i = c_i \circ q_i$. Such $q$ is epi {\color{red}{dimostrare}}, and thus $(A, B, C, s, t, q)$ is the colimit of $D$. {\color{red}{rifinire, dimostrare unicità}}.

@@

\begin{proof}
	In lieu of \Cref{lem:stab}, it is enough to proof that, given a cube as the one below, with pullbacks as back faces, pushouts as bottom and top faces and such that $h$ is a regular mono, the front faces are pullbacks too, where $\graph{G}_i = (A_i, B_i, C_i, s_i, t_i, q_i)$, $\graph{G}'=(A_i', B_i', C_i', s_i', t_i', q_i')$, for $i = 1, 2, 3, 4$.
        \[\begin{tikzcd}[row sep=23, column sep =23]
        & {\mathcal{G}_1'} && {\mathcal{G}_2'} \\
        {\mathcal{G}_3'} && {\mathcal{G}_4'} \\
        & {\mathcal{G}_1} && {\mathcal{G}_2} \\
        {\mathcal{G}_3} && {\mathcal{G}_4}
        \arrow["{h'}", from=1-2, to=1-4]
        \arrow["{k'}"', from=1-2, to=2-1]
        \arrow["b"'{pos=0.7}, from=1-2, to=3-2]
        \arrow["{t'}", from=1-4, to=2-3]
        \arrow["c", from=1-4, to=3-4]
        \arrow["{p'}"{pos=0.8}, from=2-1, to=2-3, crossing over]
        \arrow["a"', from=2-1, to=4-1]
        \arrow["h"{pos=0.7}, from=3-2, to=3-4]
        \arrow["d"'{pos=0.7}, from=2-3, to=4-3, crossing over]
        \arrow["k"', from=3-2, to=4-1]
        \arrow["t", from=3-4, to=4-3]
        \arrow["p"', from=4-1, to=4-3]
        \end{tikzcd}\]
        By \Cref{prop:eqgrph_complete} and \Cref{cor:mono_in_EqGrph}, the following two cubes have $\mathcal{M}$-pushouts as bottom faces and pullbacks as back faces, thus their front faces are pullbacks too.
        \[\begin{tikzcd}[row sep=20, column sep = 20]
        & {A_1'} && {A_2'} \\
        {A_3'} && {A_4'} \\
        & {A_1} && {A_2} \\
        {A_3} && {A_4}
        \arrow["{h'_V}", from=1-2, to=1-4]
        \arrow["{k'_V}"', from=1-2, to=2-1]
        \arrow["{b_V}"'{pos=0.7}, from=1-2, to=3-2]
        \arrow["{t'_V}", from=1-4, to=2-3]
        \arrow["{c_V}", from=1-4, to=3-4]
        \arrow["{p'_V}"{pos=0.8}, from=2-1, to=2-3, crossing over]
        \arrow["{a_V}"', from=2-1, to=4-1]
        \arrow["{h_V}"{pos=0.7}, from=3-2, to=3-4]
        \arrow["{d_V}"'{pos=0.7}, from=2-3, to=4-3, crossing over]
        \arrow["{k_V}"', from=3-2, to=4-1]
        \arrow["{t_V}", from=3-4, to=4-3]
        \arrow["{p_V}"', from=4-1, to=4-3]
        \end{tikzcd}\qquad
        \begin{tikzcd}[row sep=20, column sep = 20]
        & {B_1'} && {B_2'} \\
        {B_3'} && {B_4'} \\
        & {B_1} && {B_2} \\
        {B_3} && {B_4}
        \arrow["{h'_E}", from=1-2, to=1-4]
        \arrow["{k'_E}"', from=1-2, to=2-1]
        \arrow["{b_E}"'{pos=0.7}, from=1-2, to=3-2]
        \arrow["{t'_E}", from=1-4, to=2-3]
        \arrow["{c_E}"', from=1-4, to=3-4]
        \arrow["{p'_E}"{pos=0.8}, from=2-1, to=2-3, crossing over]
        \arrow["{a_E}"', from=2-1, to=4-1]
        \arrow["{h_E}"{pos=0.7}, from=3-2, to=3-4]
        \arrow["{d_E}"'{pos=0.7}, from=2-3, to=4-3, crossing over]
        \arrow["{k_E}"', from=3-2, to=4-1]
        \arrow["{t_E}", from=3-4, to=4-3]
        \arrow["{p_E}"', from=4-1, to=4-3]
        \end{tikzcd}
        \]

>>>>

\begin{obs}\label{obs:eq_grph_morph_det_by_first_two_comp}
    Morphisms of graphs with equivalences are uniquely determined by the first two component. That is, if $h_1 = (h_E, h_V, \phi)$ and $h_2 = (h_E, h_V, \psi)$, then $\phi = \psi$.
\end{obs}

@@

	Therefore, the outer part of the rectangle below commutes, and by \Cref{prop:prop_epi_mono_Set} there exists a unique $\tau_C: G \to Q$
    \[
        \begin{tikzcd}
            F \arrow[r, "{\tau_V}"] \arrow[d, "c"swap] & B \arrow[r, "q"] & Q \arrow[d, "m"] \\
            G \arrow[urr, dashed, "{\tau_C}"] \arrow[rr, "{\tau}"swap] & & L
        \end{tikzcd}
    \]
     Faithfulness of $U$ and \Cref{obs:eq_grph_morph_det_by_first_two_comp} guarantees that $(\tau_E, \tau_V, \tau_C)$ is the unique arrow such that $(\pi_E^i, \pi_V^i, \pi_C^i) \circ (\tau_E, \tau_V, \tau_C) = (\tau_E^i, \tau_V^i, \tau_C^i)$.

     For colimits, let $(A, B, s, t)$ be the colimit of $U \circ D$, together with morphisms $(\kappa_i)_{i \in \cat I} = (\kappa_E^i, \kappa_V^i)_{i \in \cat I}$, and suppose $((c_i)_{i \in \cat I}, C)$ be the colimit of $V \circ D$. Then, we have the following situation
     \[
	     \begin{tikzcd}[row sep = 25, column sep=25]
			& B & \\
			B_i \ar[rr, "{h_V}"] \ar[ur, "{\kappa_V^i}"] \ar[d, "{q_i}"swap] & & B_j \ar[ul, "{\kappa_V^j}"swap] \ar[d, "q_j"] \\
			C_i \ar[rr, "{h_C}" swap] \ar[dr, "{c_i}"swap] & & C_j \ar[dl, "{c_j}"] \\
			& C &
		\end{tikzcd}
     \]
     Then, $((c_i \circ q_i)_{i \in \cat I}, C)$ is a cocone for all $B_i$, and, since $((\kappa_i)_{i \in \cat I}, B)$ is the colimit of all $B_i$ (\Cref{lemma:limits_of_presheaves}), there exists a unique arrow $q: B \to C$ such that, for each $i$, $q \circ \kappa_V^i = c_i \circ q_i$. Such $q$ is epi, by application of \Cref{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}, and thus $(A, B, C, s, t, q)$, together with arrows $(\kappa_E^i, \kappa_V^i, c_i)_{i \in \cat I}$ is the colimit of $D$.

@@

\begin{proof}
	In lieu of \Cref{lemma:stab}, it is enough to proof that, given a cube as the one below, with pullbacks as back faces, pushouts as bottom and top faces and such that $h$ is a regular mono, the front faces are pullbacks too, where $\graph{G}_i = (A_i, B_i, C_i, s_i, t_i, q_i)$, $\graph{G}'=(A_i', B_i', C_i', s_i', t_i', q_i')$, for $i = 1, 2, 3, 4$.
        \[\begin{tikzcd}[row sep=23, column sep =23]
        & {\mathcal{G}_1'} && {\mathcal{G}_2'} \\
        {\mathcal{G}_3'} && {\mathcal{G}_4'} \\
        & {\mathcal{G}_1} && {\mathcal{G}_2} \\
        {\mathcal{G}_3} && {\mathcal{G}_4}
        \arrow["{h'}", from=1-2, to=1-4]
        \arrow["{k'}"', from=1-2, to=2-1]
        \arrow["b"'{pos=0.7}, from=1-2, to=3-2]
        \arrow["{t'}", from=1-4, to=2-3]
        \arrow["c", from=1-4, to=3-4]
        \arrow["{p'}"{pos=0.8}, from=2-1, to=2-3, crossing over]
        \arrow["a"', from=2-1, to=4-1]
        \arrow["h"{pos=0.7}, from=3-2, to=3-4]
        \arrow["d"'{pos=0.7}, from=2-3, to=4-3, crossing over]
        \arrow["k"', from=3-2, to=4-1]
        \arrow["t", from=3-4, to=4-3]
        \arrow["p"', from=4-1, to=4-3]
        \end{tikzcd}\]
        By \Cref{prop:eqgrph_complete} and \Cref{cor:mono_in_EqGrph}, the following two cubes have $\mathcal{M}$-pushouts as bottom faces and pullbacks as back faces, thus their front faces are pullbacks too.
        \[\begin{tikzcd}[row sep=20, column sep = 20]
        & {A_1'} && {A_2'} \\
        {A_3'} && {A_4'} \\
        & {A_1} && {A_2} \\
        {A_3} && {A_4}
        \arrow["{h'_V}", from=1-2, to=1-4]
        \arrow["{k'_V}"', from=1-2, to=2-1]
        \arrow["{b_V}"'{pos=0.7}, from=1-2, to=3-2]
        \arrow["{t'_V}", from=1-4, to=2-3]
        \arrow["{c_V}", from=1-4, to=3-4]
        \arrow["{p'_V}"{pos=0.8}, from=2-1, to=2-3, crossing over]
        \arrow["{a_V}"', from=2-1, to=4-1]
        \arrow["{h_V}"{pos=0.7}, from=3-2, to=3-4]
        \arrow["{d_V}"'{pos=0.7}, from=2-3, to=4-3, crossing over]
        \arrow["{k_V}"', from=3-2, to=4-1]
        \arrow["{t_V}", from=3-4, to=4-3]
        \arrow["{p_V}"', from=4-1, to=4-3]
        \end{tikzcd}\qquad
        \begin{tikzcd}[row sep=20, column sep = 20]
        & {B_1'} && {B_2'} \\
        {B_3'} && {B_4'} \\
        & {B_1} && {B_2} \\
        {B_3} && {B_4}
        \arrow["{h'_E}", from=1-2, to=1-4]
        \arrow["{k'_E}"', from=1-2, to=2-1]
        \arrow["{b_E}"'{pos=0.7}, from=1-2, to=3-2]
        \arrow["{t'_E}", from=1-4, to=2-3]
        \arrow["{c_E}"', from=1-4, to=3-4]
        \arrow["{p'_E}"{pos=0.8}, from=2-1, to=2-3, crossing over]
        \arrow["{a_E}"', from=2-1, to=4-1]
        \arrow["{h_E}"{pos=0.7}, from=3-2, to=3-4]
        \arrow["{d_E}"'{pos=0.7}, from=2-3, to=4-3, crossing over]
        \arrow["{k_E}"', from=3-2, to=4-1]
        \arrow["{t_E}", from=3-4, to=4-3]
        \arrow["{p_E}"', from=4-1, to=4-3]
        \end{tikzcd}
        \]
